Online appendix for "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-04-30 manuscript/appendix.qmd
Use tikz PDF in PDFs

font_opts <- list(
  extra.preamble = c(
    "\\usepackage{libertine}",
    "\\usepackage{libertinust1math}"
  ),
  # dvisvgm.opts = "--font-format=woff"
  dvisvgm.opts = "--no-fonts"
)
```

@@

plot_priors <- p1 | p2
plot_priors
# ggsave("submissions/plot_priors.svg", plot_priors, width = 6.5, height = 2.5)
```

>>>>

# Conditional tikz output types; use PDF if this is LaTeX, otherwise use SVG with outlined fonts
if (fmt_out == "latex") {
  knitr::opts_template$set(
    tikz_settings = list(
      fig.ext = "pdf", 
      fig.align = "center", 
      extra.preamble = c(
        "\\usepackage{libertine}",
        "\\usepackage{libertinust1math}"
      )
    )
  )
} else {
  knitr::opts_template$set(
    tikz_settings = list(
      fig.ext = "svg", 
      fig.align = "center", 
      extra.preamble = c(
        "\\usepackage{libertine}",
        "\\usepackage{libertinust1math}"
      ),
      engine.opts = list(dvisvgm.opts = "--no-fonts")
    )
  )
}
```

@@

plot_priors <- p1 | p2
plot_priors
# ggsave("submissions/figs/plot_priors.svg", plot_priors, width = 6.5, height = 2.5)
```
